### 2023-02-14 paper-thesis/chapters/03-background-dependent-types.tex
Chapter transitions

The \textit{Calculus of Constructions} is the language that has all three of these features, it will be implemented in chapter~\ref{chap:baselang}.

>>>>

The \textit{Calculus of Constructions} is the language that has all three of these features. Now that we have explained the concepts behind Spoofax and Dependent Types, we will further explain the Calculus of Constructions and implement it in Spoofax in chapter~\ref{chap:baselang}. Then in the chapters after that, we will extend the language with more features.

### 2023-02-14 paper-thesis/chapters/10-coc.tex
Syntax highlighting
Fix a few details
Chapter transitions

\begin{figure}[h]
\begin{lstlisting}
Expr.Type = "Type"
Expr.Var = ID
Expr.FnType = ID ":" Expr "->" Expr {right}
Expr.FnConstruct = "\\" ID ":" Expr "." Expr
Expr.FnDestruct = Expr Expr {left}
Expr.Let = "let" ID "=" Expr ";" Expr
\end{lstlisting}
\caption{The concrete syntax for the base language. $\co{FnConstruct}$ is a lambda function, $\co{FnDestruct}$ is application of a lambda function.}
\label{fig:syntax}
\end{figure}

@@

An additional benefit of Krivine machines is that the run-time performance of them tends to be a bit higher, though this is only a constant factor and not a time-complexity improvement.

@@

>>>>

\begin{figure}[h]
\lstset{language=SDF3}
\begin{lstlisting}
Expr.Type = "Type"
Expr.Var = ID
Expr.FnType = ID ":" Expr "->" Expr {right}
Expr.FnConstruct = "\\" ID ":" Expr "." Expr
Expr.FnDestruct = Expr Expr {left}
Expr.Let = "let" ID "=" Expr ";" Expr
\end{lstlisting}
\lstset{language=base}
\caption{The concrete syntax for the base language. $\co{FnConstruct}$ is a lambda function, $\co{FnDestruct}$ is application of a lambda function.}
\label{fig:syntax}
\end{figure}

@@

An additional benefit of Krivine machines is that the run-time performance of them tends to be a bit better, though this is only a constant factor and not a time-complexity improvement.

@@

We now have an implementation of the Calculus of Constructions in Spoofax. This implementation still has the issue of variable capture, which we will discuss and solve on chapter \ref{chap:namecolls}. Next, from chapter \ref{chap:bools} onward we will show how to extend the language.
